Comparative Analysis of Discount Rates Across Grocery Vendors

### 2024-11-14 paper/paper.qmd
final update

---
title: "Comparative Analysis of Discount Rates Across Grocery Vendors"
author: 
  - Ariel Xing - Xinxiang Gao - John Zhang -Haoan Wang 
thanks: "Code and data are available at: https://github.com/Jiaqi-Xing/Grocery-Prices-analysis"
date: today
date-format: long
abstract: "This study examines discount rate patterns among major grocery vendors, analyzing how discount levels vary by vendor and over time. By comparing average discount rates and observing monthly trends, the research highlights notable differences in both the overall discount levels and monthly discounting patterns among vendors. Additionally, a deeper examination reveals evidence of Simpson's Paradox, where aggregated discount trends obscure unique, vendor-specific monthly patterns. These findings provide a clearer understanding of retailer discounting practices, illustrating how vendors balance pricing strategies to attract consumers. This research is important as it informs consumers and businesses on discount dynamics, supporting more informed decision-making in the retail market."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

Understanding these trends is important for retailers, consumers, and policymakers as it sheds light on the dynamics of discount strategies. For consumers, knowing which vendors offer higher or more stable discounts can guide purchasing decisions. For retailers, recognizing competitive discounting patterns can inform pricing strategies to attract customers. For policymakers, identifying discount trends can reveal aspects of market competitiveness and economic trends within the retail sector. The remainder of this paper is structured as follows: in @sec-data, we describe the dataset in detail, including the context, variables, and measurement approach used to capture real-world phenomena; in @sec-result, we examine the results, presenting key findings through graphs, tables, and statistical analysis; in @sec-discussion, we discuss the implications of our findings, addressing issues such as correlation versus causation, missing data, and potential sources of bias.
# Data {#sec-data}

@@

Our data source [@data] was prepared using the SQLite programming language [@sqlite] to facilitate efficient handling and querying. Data simulation, testing, and visualization were performed using R [@citeR], with support from the packages readr [@readr] for data import, ggplot2 [@ggplot2] for plotting, and tidyverse [@tidyverse] for data manipulation. Inspired by the methods discussed in "Telling Stories with Data" [@tellingstories], we applied Simpson's Paradox to explore complex trends and relationships in our analysis.

>>>>

---
title: "Comparative Analysis of Discount Rates Across Grocery Vendors"
author: 
  - Ariel Xing 
  - Xinxiang Gao 
  - John Zhang 
  - Haoan Wang 
thanks: "Code and data are available at: https://github.com/Jiaqi-Xing/Grocery-Prices-analysis"
date: today
date-format: long
abstract: "This study examines discount rate patterns among major grocery vendors, analyzing how discount levels vary by vendor and over time. By comparing average discount rates and observing monthly trends, the research highlights notable differences in both the overall discount levels and monthly discounting patterns among vendors. Additionally, a deeper examination reveals evidence of Simpson's Paradox, where aggregated discount trends obscure unique, vendor-specific monthly patterns. These findings provide a clearer understanding of retailer discounting practices, illustrating how vendors balance pricing strategies to attract consumers. This research is important as it informs consumers and businesses on discount dynamics, supporting more informed decision-making in the retail market."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

Understanding these trends is important for retailers, consumers, and policymakers as it sheds light on the dynamics of discount strategies. For consumers, knowing which vendors offer higher or more stable discounts can guide purchasing decisions. For retailers, recognizing competitive discounting patterns can inform pricing strategies to attract customers. For policymakers, identifying discount trends can reveal aspects of market competitiveness and economic trends within the retail sector. The remainder of this paper is structured as follows: in @sec-data, we describe the dataset in detail, including the context, variables, and measurement approach used to capture real-world phenomena; in @sec-result, we examine the results, presenting key findings through graphs, tables, and statistical analysis; in @sec-discussion, we discuss the implications of our findings, addressing issues such as correlation versus causation, missing data, and potential sources of bias.

# data {#sec-data}

@@

Our data source [@data] was prepared using the SQLite programming language [@sqlite] to facilitate efficient handling and querying. Data simulation, testing, and visualization were performed using R [@citeR], with support from the packages readr [@readr], ggplot2 [@ggplot2], tidyverse [@tidyverse], dplyr[@dplyr], validate[@validate]. Inspired by the methods discussed in "Telling Stories with Data" [@tellingstories], we applied Simpson's Paradox to explore complex trends and relationships in our analysis.
